Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-30 paper.qmd
Updated axes
Fixed size of Figure 11

axes_obj <- gen_axes(
  data = scaled_gau_data,
  proj_data = projected_df,
  limits = 0.2,
  axis_pos_x = -0.12,
  axis_pos_y = -0.12)

@@

axes_obj <- gen_axes(
  data = scaled_gau_data,
  proj_data = projected_df,
  limits = 0.2,
  axis_pos_x = 0.45,
  axis_pos_y = -0.28)

@@

```{r}
#| label: fig-five-gau-nldr-layouts
#| fig-height: 10
#| fig-width: 15
#| fig-pos: H
#| fig-cap: "(a) tSNE, (b) UMAP, and (c) PaCMAP"

@@

```{r}
#| label: fig-five-gau-projs
#| fig-height: 15
#| fig-width: 10
#| fig-pos: H
#| fig-cap: "(a) tSNE, (b) UMAP, and (c) PaCMAP"

>>>>

@@

@@

```{r}
#| label: fig-five-gau-nldr-layouts
#| fig-height: 5
#| fig-width: 15
#| fig-pos: H
#| fig-cap: "(a) tSNE, (b) UMAP, and (c) PaCMAP"

@@

```{r}
#| label: fig-five-gau-projs
#| fig-height: 10
#| fig-width: 15
#| fig-pos: H
#| fig-cap: "(a) tSNE, (b) UMAP, and (c) PaCMAP"
